Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-03-10 src/tex/ms.tex
190521 wip

GW190521 is the most extreme representative of a class of events with bimodal $\kappa$ posteriors (Table \ref{tab:bimodal_events_mass}).
As we anticipated in Sec.~\ref{sec:inclination}, this is driven by not having sufficient frequencies in band to disambiguate between $\kappa$ and $\cos\iota$.
As the most massive \ac{BBH} in our set, GW190521 is also the one with the fewest cycles in band, and therefore the most susceptible to this degeneracy.

>>>>

GW190521 is the most extreme representative of a class of events with bimodal $\kappa$ posteriors (Table \ref{tab:bimodal_events_mass}).
This appears to arise out of a confluence of factors related to this event's high mass and support for precession: this being the most massive event in our set, the signal is only in-band for a very short time before merger, meaning that spin effects can more easily be approximated by frequency-dependent birefringent.
In particular, a precession cycle can more easily by approximated by a monotonic amplitude modulation.
This effect gives rise to a similar degeneracy between $\kappa$ and $\chi_p$ as outlined for GW170818, wherein the prior volume favored configurations with $|\kappa| >0$.
However, in the case of GW190521, the polarization measurement at the detectors is not accurate enough to fully disambiguate between right- and left-handed states (as implied by the bimodal $\cos\iota$ posterior obtained assuming \ac{GR} in Fig.~\ref{fig:corner_GW190521}).
As a result, the $\kappa$ posterior is bimodal for GW190521.
